---
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: 
  bookdown::pdf_document2:
    toc: no
geometry: margin = 1in
fontsize: 12pt
bibliography: library.bib
csl: apa.csl
link-citations: yes
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \setlength{\parindent}{1em}
- \doublespacing
- \usepackage{float}
- \usepackage{amsmath}
- \DeclareMathOperator{\logit}{logit}
---

\pagenumbering{gobble}

```{r knitr.global_options, include=F}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='images/', echo=FALSE, warning=FALSE, message=FALSE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```



```{r child = '001-title.Rmd'}
```
\newpage
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}
\pagestyle{fancy}
\pagenumbering{arabic}
\setcounter{tocdepth}{3}
\linespread{1}\selectfont
\tableofcontents
\newpage

```{r child = '002-introduction.Rmd'}
```

\FloatBarrier
\newpage


```{r child = '003-literature.Rmd'}
```
\FloatBarrier
\newpage

```{r child = '004-methodology.Rmd'}
```
\FloatBarrier
\newpage

```{r child = '005-data.Rmd'}
```
\newpage
\linespread{1.0}\selectfont
```{r child = '009-appendices.Rmd'}
```

\FloatBarrier
\newpage

\linespread{1.0}\selectfont

# References
# Bibliography
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent


<div id="refs"></div>
