---
title: "Appendices"
date: "12.11-2020"
output: 
  bookdown::pdf_document2:
    toc: no
csl: apa5th.csl
bibliography: library.bib
indent: yes
fontsize: 12pt
geometry: margin = 1in
link-citations: yes
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{float}
- \usepackage{amsmath}
- \DeclareMathOperator{\logit}{logit}
---

# Appendices
```{r run libraries, include=F}
library(stringr)
library(tidyverse)
library(summarytools)
library(kableExtra)
library(dynlm)
library(stats)
library(readr)
library(dplyr)
library(ggplot2)
library(data.table)
library(MacroRF)
require(data.table)
library(zoo)
```


```{r Import Data, include=F}
df <- read_csv("data/gdp_yiv.csv")
dependent<- read_csv("data/dependent.csv")
feds <- read_csv("data/feds.csv")
```

```{r Date formatting, include=F}
#Re-format Date
df$Date <- str_c(df$Date,"/01")
df$Date <- as.Date(df$Date,format = "%Y/%m/%d")
```

```{r Log Change for GDP, include=F}
no_lags <- 4 
df <- df %>%
  mutate(log_gdp=log(1+GDP))

df <- df %>%
  arrange %>%
    mutate(H12=rollapply(log_gdp, 4,FUN=mean, na.rm = TRUE, fill = NA, align = "right" )) %>%
      mutate(H18=rollapply(log_gdp, 6,FUN=mean, na.rm = TRUE, fill = NA, align = "right" )) %>%
        mutate(H24=rollapply(log_gdp, 8,FUN=mean, na.rm = TRUE, fill = NA, align = "right" )) %>%
          mutate(H30=rollapply(log_gdp, 10,FUN=mean, na.rm = TRUE, fill = NA, align = "right" ))
```


```{r Regression output to Dataframe, include=F}
# define a function to get coefficients from linear regression
  
do_regression <- function(var)
  { # var - the name of the variable to be regressed
    res <- lm(as.formula(paste0(var, "~ YIV")), df) # run linear regression
    coefs <- c("R-Squared"= summary(res)$r.squared*100, "Intercept" = summary(res)$coefficients[1], "Beta" = summary(res)$coefficients[2], "t-statistic" = summary(res)$coefficients[,3]) 
  return(coefs)
  }

df_results <- as.data.frame(t(sapply(colnames(df)[5:7], do_regression)))
#sapply : applies on "var3"(first YIV) ..."var23"(last)  the function do_lm
#t() transposes

df_results <- df_results %>%
  round(2)
```

```{r Summary Statistics, include=F}

statistics_GDP <- df %>%
  select(GDP, YIV) %>%
    descr(
      transpose=TRUE,
      stats = c("mean","sd","min","q1","med","q3","max","n.valid"))

statistics_feds <- feds %>%
  select (SVEN1F01) %>%
    descr(
      transpose=TRUE,
      stats = c("mean","sd","min","q1","med","q3","max","n.valid"))

statistics_dependent <- dependent %>%
  select (EMP, IND, CON) %>%
    descr(
      transpose=TRUE,
      stats = c("mean","sd","min","q1","med","q3","max","n.valid"))


statistics <- t(cbind( t(statistics_GDP[nrow(statistics_GDP):1,]), t(statistics_dependent), t(statistics_feds)))

```




## Appendix A
Notes: This table includes summary statistics for main variables used in our research. Statistics include mean, median, min, max, standard deviation, etc. In Panel A, blablaba. In Panel B, the regressors are listed. In Panel C, control variables are listed

```{r Table summary, message = F, warnings = F, echo = F}

kbl(cbind(statistics), booktabs = T,  longtable=T, align="c", digits=2, caption="Summary Statistics") %>%
  kable_styling(latex_options = c("striped","repeat_header")) %>%
    pack_rows("Panel A: YIV",1,1, latex_align="c") %>%
      pack_rows("Panel B: Dependent Variables",2,5, latex_align="c") %>%
        pack_rows("Panel C: Control Variables",6,6, latex_align="c") %>%
          footnote(general = "Currently SVENF01 denotes interest rates that will be converted to changes in term spread. ",
          number = c("Footnote 1; ", "Footnote 2; "),
)

  

```
\newpage


## Appendix B. 
Notes: This table includes regression using GDP & YIV, control variables & other stuff. The equation for the regression is the following:
\begin{equation}
\sum_{j=1}^{j=H}log(1+GDP_{i,t+j})/H = \alpha_{H}+ \beta_{H} \sigma_{IV,t}^{INT} + Controls +\varepsilon_{t+H}
\end{equation}

```{r Table OLS, message = F, warnings = F,echo = F}
kbl(cbind(t(df_results)), booktabs = T, longtable=T, align="c", digits=2, caption="Regression output") %>%
   kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
     pack_rows("Panel A: YIV",1,3, latex_align="c") %>%
       footnote(general = "Reference?")

```
\newpage

## Appendix C
```{r GDP_YIV, message=F, warnings=F,echo = F, fig.cap="GDP Growth(%) vs 5-year Treasury Implied Volatility"}
par(mar = c(5, 5, 3, 5))
plot(df$Date, df$YIV, type = "l", xlab = "Date", ylab = "YIV (%)", col = "blue", main = "GDP growth vs YIV")
par(new=TRUE)
plot(df$Date, df$GDP, type = "l", xaxt = "n", yaxt = "n", xlab = "", ylab = "", col = "red", lty = 2)
axis(side = 4)
mtext("GDP growth(%)", side = 4, line = 3)
legend("topleft", c("YIV", "GDP"),
       col = c("blue", "red"), lty = c(1, 2))
```





