---
title: "Appendices"
date: "12.11-2020"
output: 
  bookdown::pdf_document2:
    toc: no
csl: apa.csl
bibliography: library.bib
indent: yes
fontsize: 12pt
geometry: margin = 1in
link-citations: yes
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{float}
- \usepackage{amsmath}
- \DeclareMathOperator{\logit}{logit}
---

```{r, include=F}
source("functions.R")
```


# Appendices

## Appendix A

As researchers typically do not typically post underlying data with their research, various plot digitizers have seen an exponential increase in use. @Drevon2017 researched intercoder reliability, during which over 3500 data points were extracted with WebPlotDigitizer from 36 different graphs. Nevertheless, they controlled the validity of the results and concluded that there was a near perfect correlation (r=0.989 with p-value <0.01) between extracted and actual data. Nevertheless, the limitations mentioned highlight coders previous experience with plot-digitizing tools.

Furthermore, @Burda2017 also highlight that systematic reviewers often tend to have data constraints which is why plot digitizers are of a great help. They estimated data using WebPlotDigitizer and conclude that the extraction done by different coders was consistent; nevertheless, in the case of continuous data (compared to event data), the distribution varied more. Whatsoever, the intreclass coefficient for both types of plots was over 95%.

We also used the WebPlotDigitzer in our research and as validity test extracted GDP from the same graph as YIV time series & plotted it with actuals - see the graph below.



```{r vsextracted, message=F, warnings=F,echo = F, fig.height=5, fig.cap="Actual vs Extracted GDP growth rate in %"}
GDP_data <- read_csv("data/actualvsplot.csv")

extracted <- ggplot(GDP_data,aes(x=Date)) + geom_line(aes(y=Actual, color="Actual"), color="red") + geom_line(aes(y=Extracted, color="Extracted"), color="blue") +theme_bw() + ylab("GDP growth %") + theme_bw()

extracted

```


\newpage
## Appendix B
```{r regfit, message = F, warnings = F, echo = F, fig.height=2.5, fig.width=6, fig.cap="Regressions' R-squared"}
regr1 <- regrs(mudelid=c("YIV"))
results1 <- regr_results(a=regr1)
results1 <- as.data.frame(t(results1))

regression.fit <- ggplot(results1, aes(x=row.names(results1),y=r.squared)) + geom_bar(stat="identity", fill="steelblue")+ theme_minimal() + xlab("Quarters") + ylab("R-squared") + labs(title = "GDP R-squared") +  theme(plot.title = element_text(hjust = 0.5)) + scale_x_discrete(limits=c("H4", "H6", "H8", "H10", "H12"))

regression.fit
```



```{r regcoefficients, message = F, warnings = F, echo = F, fig.height=3, fig.width=6, fig.cap="Regressions' coefficients"}

regression.coefficients <- ggplot(results1, aes(x=row.names(results1), y=YIV_estimate))+ geom_bar(stat="identity", fill="steelblue")+theme_minimal()+ xlab("Quarters") + ylab("Coefficients") + labs(title = "GDP coefficients") + theme(plot.title = element_text(hjust = 0.5)) + scale_x_discrete(limits=c("H4", "H6", "H8", "H10", "H12"))

regression.coefficients

```


\newpage
## Appendix C
```{r GDPvsYIV, message=F, warnings=F, echo = F, fig.cap="GDP Growth(%) vs 5-year Treasury Implied Volatility"}
par(mar = c(5, 5, 3, 5))
plot(df$Date, df$YIV, type = "l", xlab = "Date", ylab = "YIV (%)", col = "blue", main = "GDP growth vs YIV")
par(new=TRUE)
plot(df$Date, df$GDP, type = "l", xaxt = "n", yaxt = "n", xlab = "", ylab = "", col = "red", lty = 2)
axis(side = 4)
mtext("GDP growth(%)", side = 4, line = 3)
legend("topleft", c("YIV", "GDP"),
       col = c("blue", "red"), lty = c(1, 2))
```


\newpage
## Appendix D

Notes: This table includes regression with controls. The equation for the regression is following:

\begin{equation}
\sum_{j=1}^{j=H}log(1+GDP_{i,t+j})/H = \alpha_{H}+ \beta_{H} \sigma_{IV,t}^{INT} +\varepsilon_{t+H}
\end{equation}



```{r OLS4, message = F, warnings = F,echo = F}
regr4 <- regrs(mudelid=c("DGS1","TRM1012", "SRT03M", "baa_aaa", "VIX", "housng", "gz_spr", "spy_logreturn"))
results4 <- regr_results(a=regr4)

results4  %>%
  kbl(booktabs = T,longtable=T, align="c", digits=2, caption="Regression with state-dependency") %>%
   kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
   column_spec(1:1, width="2in")%>%
       footnote(general = "*** - p<0.01, ** - p<0.05, * - p<0.1. Reported standard error is adjusted for heteroskedasticity")

#model4 <- lm(log_gdp ~ lag1 + lag2 + DGS1 + TRM1012 + SRT03M + baa_aaa + VIX + housng + gz_spr + spy_logreturn, df)
#ols_vif_tol(model4)
```

\newpage
## Appendix E

Notes: YIV, dummy and controls as independent variables. The equation for the regression is following:

\begin{equation}
\sum_{j=1}^{j=H}log(1+GDP_{i,t+j})/H = \alpha_{H}+ \beta_{H} \sigma_{IV,t}^{INT} +\varepsilon_{t+H}
\end{equation}



```{r OLS5, message = F, warnings = F,echo = F}
regr5 <- regrs(mudelid=c("YIV", "dum", "DGS1", "TRM1012", "SRT03M", "baa_aaa", "VIX", "housng", "gz_spr", "spy_logreturn"))
results5 <- regr_results(a=regr5)

results5  %>%
  kbl(booktabs = T,longtable=T, align="c", digits=2, caption="Regression with state-dependency") %>%
   kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
    column_spec(1:1, width="2in")%>%
       footnote(general = "*** - p<0.01, ** - p<0.05, * - p<0.1. Reported standard error is adjusted for heteroskedasticity")

#model5 <- lm(log_gdp ~ YIV + dum + YIV*dum + lag2 + DGS1 + TRM1012 + SRT03M + baa_aaa + VIX + housng + gz_spr + spy_logreturn, df)
#ols_vif_tol(model5)

# model6 <- lm(log_gdp ~  YIV + dum + YIV*dum + lag1 + lag2 + DGS1 + TRM1012 + SRT03M + baa_aaa + VIX + housng + gz_spr + spy_logreturn, df)
# ols_step_forward_p(model6)
# ols_step_best_subset(model6)
# ols_step_all_possible(model6)

```
\newpage

## Appendix F


```{r roll_regress, message = F, warnings = F,echo = F, }

df_resultss %>%
  kbl(longtable=T, booktabs=T) %>%
  kable_styling() 
```



```{r oosgraph, message = F, warnings = F,echo = F, fig.height=3, fig.cap="Out-of-sample RMSFE for various estimations"}
df_results <- transpose(df_resultss)
df_resultss2 <- melt(df_resultss)
df_resultss2$rowid <- c("YIV", "YIV_Recessionary", "YIV_Expansionary" ,"Naive", "Naive_Recessionary", "Naive_Expansionary", "TRM", "CRS")

ggplot(df_resultss2, aes(variable, value, group=factor(rowid))) + geom_line(aes(color=factor(rowid))) + theme_bw() + theme(legend.position = "bottom") + labs(x="Time horizon", y="RMSFE value", color="Model")


```

\newpage
<<<<<<< HEAD
## Appendix G^[Full R-Code with data is available upon request in github repository: https://github.com/karelrappo/thesis2020]
=======
## Appendix I^[Full R-Code with data is available upon request in github repository: https://github.com/karelrappo/thesis2020]
>>>>>>> ea9f25ee71faf8682581c96cfc785af36a67aeff


```{r rfjoonised1, figures-side, fig.show="hold", out.width="50%", echo = F}

plot1 <- results(c("ols", "rf"))
plot2 <- results(c("ols_rec", "rf_rec"))
plot3 <- results(c("ols_exp", "rf_exp"))
plot1
plot2
plot3

```


