---
title: "Appendices"
date: "12.11-2020"
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
csl: apa.csl
bibliography: library.bib
indent: yes
fontsize: 12pt
geometry: margin = 1in
link-citations: yes
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{float}
- \usepackage{amsmath}
- \DeclareMathOperator{\logit}{logit}
---

```{r, include=F}
source("functions.R")
```


# Appendices

## Appendix A

As researchers typically do not typically post underlying data with their research, various plot digitizers have seen an exponential increase in use. @Drevon2017 researched intercoder reliability, during which over 3500 data points were extracted with WebPlotDigitizer from 36 different graphs. Nevertheless, they controlled the validity of the results and concluded that there was a near perfect correlation (r=0.989 with p-value <0.01) between extracted and actual data. Nevertheless, the limitations mentioned highlight coders previous experience with plot-digitizing tools.

Furthermore, @Burda2017 also highlight that systematic reviewers often tend to have data constraints which is why plot digitizers are of a great help. They estimated data using WebPlotDigitizer and conclude that the extraction done by different coders was consistent; nevertheless, in the case of continuous data (compared to event data), the distribution varied more. Whatsoever, the intreclass coefficient for both types of plots was over 95%.

We also used the WebPlotDigitzer in our research and as validity test extracted GDP from the same graph as YIV time series & plotted it with actuals - see the graph below.



```{r vsextracted, message=F, warnings=F,echo = F, fig.height=5, fig.cap="Actual vs Extracted GDP growth rate in %"}
GDP_data <- read_csv("data/actualvsplot.csv")

extracted <- ggplot(GDP_data,aes(x=Date)) + geom_line(aes(y=Actual, color="Actual"), color="red") + geom_line(aes(y=Extracted, color="Extracted"), color="blue") +
  theme_bw() +
  ylab("GDP growth %") 

extracted

```


\newpage
## Appendix B

```{r regfit, message = F, warnings = F, echo = F, fig.height=2.5, fig.width=6, fig.cap="Regressions' R-squared"}
regr1 <- regrs(mudelid=c("YIV"),interaction=F)
results1 <- regr_results(a=regr1)
results1 <- as.data.frame(t(results1))
  
regression.fit <- ggplot(results1, aes(x=row.names(results1),y=r.squared))+
  geom_bar(stat="identity", fill="steelblue")+
  theme_bw() +
  xlab("Quarters") +
  ylab("R-squared") +
  labs(title = "GDP R-squared") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(limits=c("H1","H2","H4", "H8"))

regression.fit
```



```{r regcoefficients, message = F, warnings = F, echo = F, fig.height=3, fig.width=6, fig.cap="Regressions' coefficients"}

regression.coefficients <- ggplot(results1, aes(x=row.names(results1), y=YIV_estimate))+
  geom_bar(stat="identity", fill="steelblue")+
  theme_bw()+
  xlab("Quarters") +
  ylab("Coefficients") +
  labs(title = "GDP coefficients") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(limits=c("H1","H2","H4","H8"))

regression.coefficients

```


\newpage
## Appendix D

Notes: The following regressions includes YIV, dummy and controls as independent variables. The specification for the regression is the following:

\begin{equation}
\sum_{j=1}^{j=H}log(1+GDP_{i,t+j})/H = \alpha_{H}+ \beta_{H} \sigma_{IV,t}^{INT} +\varepsilon_{t+H}
\end{equation}




```{r OLS5, message = F, warnings = F,echo = F}
regr5 <- regrs(mudelid=indep_replication2,interaction=F)
results5 <- regr_results(a=regr5) %>%
  round(2) %>%
  significance() %>%
    rename(" "=rowname)



results5  %>%
  kbl(booktabs = T,longtable=T, align="c", digits=2, caption="Regression with state-dependency") %>%
   kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
    column_spec(1:1, width="2in")%>%
       footnote(general = "*** - p<0.01, ** - p<0.05, * - p<0.1. Reported standard error is adjusted for heteroskedasticity")

#model5 <- lm(log_gdp ~ YIV + dum + YIV*dum + lag2 + DGS1 + TRM1012 + SRT03M + baa_aaa + VIX + housng + gz_spr + spy_logreturn, df)
#ols_vif_tol(model5)

# model6 <- lm(log_gdp ~  YIV + dum + YIV*dum + lag1 + lag2 + DGS1 + TRM1012 + SRT03M + baa_aaa + VIX + housng + gz_spr + spy_logreturn, df)
# ols_step_forward_p(model6)
# ols_step_best_subset(model6)
# ols_step_all_possible(model6)

```
\newpage

## Appendix E


```{r, rmsfeerrors, message = F, warnings = F,echo = F}

df_resultss %>%
  kbl(longtable=T, booktabs=T) %>%
  kable_styling(full_width = TRUE) 
```


```{r, rmsfegraphs, message = F, warnings = F,echo = F}

ggplot(df_resultss2, aes(variable, value, group=factor(rowid))) +
  geom_line(aes(color=factor(rowid))) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x="Time horizon", y="RMSFE value", color="Model", caption="Naive refers to regressions with GDP and its lags, TRM - term spreads, CRS - credit spreads") +
  facet_wrap( ~rowid)
#fig.cap"Out-of-sample RMSFE for various estimations"
```
\newpage

## Appendix F

```{r, pred-vs-actual-lm, message = F, warnings = F,echo = F, fig.cap="Predicted vs actual results (Linear model)"}


pred_vs_actual_graph(lm,"Linear model") 

```

```{r, pred-vs-actual-rf, message = F, warnings = F,echo = F, fig.cap="Predicted vs actual results (Random forest)"}


pred_vs_actual_graph(rf,"Random forest")


```

\newpage
## Appendix G^[Full R-Code with data is available upon request in github repository: https://github.com/karelrappo/thesis2020]


```{r, RSMFE-lm-vs-rf, message = F, warnings = F,echo = F, fig.cap="RMSFE-s of linear model and random forest"}

ggplot(rf_resultsss, aes(variable, value, group=factor(Specification))) + geom_line(aes(color=factor(Specification))) +
  theme(legend.position="bottom") +
  labs(x="Time horizon", y="RMSFE", color="Model") + 
  facet_wrap(~period) +
  scale_color_manual(values=c("blue", "red")) +
  theme_bw()

```


\newpage
## Appendix H

```{r, sum-stat,message = F, warnings = F,echo = F}
summary_table <- colnames(df_summary)
summary_table <- summary_table %>%
  as_tibble() %>%
  rename(Variable=value)

summary_table$Description <- c("5 - year Treasury Implied Volatility",
                               "Real gross domestic product",
                               "Returns of VIX index",
                               "BAA corporate bond yields",
                               "AAA corporate bond yields",
                               "Yield spread between BAA and AAA yields",
                               "New housing market starts",
                               "Changes in 3 month treasury yield",
                               "TRM1003 - 10 year and 3 month treasury yield spread",
                               "TRM1006 - 10 year and 6 month treasury yield spread",
                               "TRM1012 - 10 year and 1 year treasury yield spread",
                               "TRM0503 - 5 year and 3 month treasury yield spread",
                               "TRM0506 - 5 year and 6 month treasury yield spread",
                               "Three month corporate bond yield")
  
summary_table %>%
  kbl(longtable=T, booktabs=T) %>%
  kable_styling() 
```

\newpage
## Appendix I


```{r, squared-errors, message = F, warnings = F,echo = F, fig.cap="Squared errors"}
a <- c("OOS_error_lm","OOS_error_rf")
squared_error_plot(a)
```

\newpage
## Appendix J

**Formula for dependent variable as used in the paper where $GDP_{t+j}$ is the GDP year-on-year growth rate in quarter $t+j$.**

\begin{align}
\label{BS_note}
\frac{1}{h}\sum_{j=1}^{j=h} \ln (1 + GDP_{t+j})
\end{align}


For $h=1$

\begin{align}
\ln (1 + GDP_{t+1}) & = \ln \left(1 + \frac{y_{t+1} - y_{t-3}}{y_{t-3}}\right) = \\
&= \ln \left(1 + \frac{y_{t+1}}{y_{t-3}-1} \right) = \ln \left(\frac{y_{t+1}}{y_{t-3}} \right) = \\
&= \ln y_{t+1} - \ln y_{t-3} = \\
&= \ln y_{t+1} - \ln y_{t} + \ln y_{t} - \ln y_{t-1} + \ln y_{t-1}  - \ln y_{t-2} + \ln y_{t-2} - \ln y_{t-3} = \\
&= (\ln y_{t+1} - \ln y_{t}) + (\ln y_{t} - \ln y_{t-1}) + (\ln y_{t-1}  - \ln y_{t-2}) + (\ln y_{t-2} - \ln y_{t-3}) = \\
&= \Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} + \Delta \ln y_{t-2}
\end{align}


For $h=2$

\begin{align}
&\frac{1}{2}( \ln (1 + GDP_{t+2}) + \ln (1 + GDP_{t+1}) ) = \\
&= \frac{1}{2}( \Delta \ln y_{t+2} + \Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} +  \Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} + \Delta \ln y_{t-2}) =\\
&= \frac{1}{2}( \Delta \ln y_{t+2} + 2\Delta \ln y_{t+1} + 2\Delta \ln y_{t} + 2\Delta \ln y_{t-1} + \Delta \ln y_{t-2}) 
\end{align}


For $h=4$

\begin{align}
&\frac{1}{4}( \ln (1 + GDP_{t+4}) + \ln (1 + GDP_{t+3}) +  \ln (1 + GDP_{t+2}) + \ln (1 + GDP_{t+1})) = \\
&= \frac{1}{4}(
\Delta \ln y_{t+4} + \Delta \ln y_{t+3} + \Delta \ln y_{t+2} + \Delta \ln y_{t+1} + \\ 
&+\Delta \ln y_{t+3} + \Delta \ln y_{t+2} + \Delta \ln y_{t+1} + \Delta \ln y_{t} +\\
&+\Delta \ln y_{t+2} + \Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} + \\
&+\Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} + \Delta \ln y_{t-2} + ) =\\
&= \frac{1}{4}( \Delta \ln y_{t+4} +2 \Delta \ln y_{t+3} + 3\Delta \ln y_{t+2} + 4\Delta \ln y_{t+1} + 3\Delta \ln y_{t} + 2\Delta \ln y_{t-1} + \Delta \ln y_{t-2}) 
\end{align}


**This formula is for h-step ahead average quarterly growth rate for $h=4$:**

\begin{align}
&\frac{1}{4}( \ln (1 + GDP_{t+4})) = \\
&= \frac{1}{4}(
\Delta \ln y_{t+4} + \Delta \ln y_{t+3} + \Delta \ln y_{t+2} + \Delta \ln y_{t+1})
\end{align}

**Formula for h-step ahead quarterly growth rate:**

\begin{align}
\Delta \ln y_{t+4} 
\end{align}

