---
title: "Appendices"
date: "12.11-2020"
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
csl: apa.csl
bibliography: library.bib
indent: yes
fontsize: 12pt
geometry: margin = 1in
link-citations: yes
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{float}
- \usepackage{amsmath}
- \DeclareMathOperator{\logit}{logit}
---

```{r, include=F, echo=F}
source("functions.R")

dep_H <- c("H1", "H8")
dep_N <- c("N1", "N8")

combiner_appendice <- function(dependent){
  combined <- data.frame(matrix(ncol = 3, nrow = 0))
  x <- c("predicted", "actuals", "Date")
  colnames(combined) <- x
  for (i in dependent){
    output <- out_of_samp2(i,indep_RMSFE,"rf") %>%
      mutate(variable=i)
      
    combined <- rbind(combined,output)
    
  }
  return(combined)
}

N <-  combiner_appendice(dep_N)
H <- combiner_appendice(dep_H)

bsnote_graph <- function(var,lab){
  ggplot(var, aes(x=as.Date(Date))) + geom_line(aes(y=predicted, color="red")) + geom_line(aes(y=actuals, color="blue"))+ theme_bw() +
    theme(legend.position="bottom",legend.title = element_blank()) + labs(x="Time horizon", y=paste0(lab)) + 
    facet_wrap(~variable) + scale_color_manual(labels = c("Actuals", "Predicted"), values = c("blue", "red")) +
    annotate("rect", xmin = as.Date("2001-04-01", "%Y-%m-%d"), xmax = as.Date("2001-10-01",  "%Y-%m-%d"), ymin = -Inf, ymax = Inf,alpha = 0.4, fill = "grey") +
    annotate("rect", xmin = as.Date("2008-01-01", "%Y-%m-%d"), xmax = as.Date("2009-04-01",  "%Y-%m-%d"), ymin = -Inf, ymax = Inf,alpha = 0.4, fill = "grey")
}
```

# Appendices
\addtocontents{toc}{\protect\setcounter{tocdepth}{-1}}
# (APPENDIX) Appendix {-}

# Appendix A {#S:digitizer} 

As researchers typically do not typically post underlying data with their research, various plot digitizers have seen an exponential increase in use. @Drevon2017 researched intercoder reliability, during which over 3500 data points were extracted with WebPlotDigitizer from 36 different graphs. Nevertheless, they controlled the validity of the results and concluded that there was a near perfect correlation (r=0.989 with p-value <0.01) between extracted and actual data. Nevertheless, the limitations mentioned highlight coders previous experience with plot-digitizing tools.

Furthermore, @Burda2017 also highlight that systematic reviewers often tend to have data constraints which is why plot digitizers are of a great help. They estimated data using WebPlotDigitizer and conclude that the extraction done by different coders was consistent; nevertheless, in the case of continuous data (compared to event data), the distribution varied more. Whatsoever, the interclass coefficient for both types of plots was over 95%.

We also used the WebPlotDigitzer in our research and as validity test extracted GDP from the same graph as YIV time series & plotted it with actuals - see the graph below.



```{r vsextracted, message=F, warnings=F,echo = F, fig.height=5, fig.cap="Actual vs Extracted GDP growth rate in %"}
GDP_data <- read_csv("data/actualvsplot.csv")

extracted <- ggplot(GDP_data,aes(x=Date)) +
  geom_line(aes(y=Actual, color="Actual")) +
  geom_line(aes(y=Extracted, color="Extracted")) +
  theme_bw() +
  ylab("GDP growth %")+
  theme(legend.position="bottom",legend.title = element_blank())

extracted

```


\newpage
# Appendix B
The following figures illustrate r-squared and coefficients for the YIV-only regression:

\begin{equation}
\frac{1}{H} \sum_{j=1}^{j=H}log(1+GDP_{i,t+j}) = \alpha_{H}+ \beta_{H} \sigma_{IV,t} +\varepsilon_{t+H}
\end{equation}

```{r regfit, message = F, warnings = F, echo = F, fig.height=2.5, fig.width=6, fig.cap="Regressions' R-squared"}
regr1 <- regrs(indep_vars=c("YIV"),interaction=F)
results1 <- regr_results(a=regr1)
results1 <- as.data.frame(t(results1))
  
regression.fit <- ggplot(results1, aes(x=row.names(results1),y=r.squared))+
  geom_bar(stat="identity", fill="steelblue")+
  theme_bw() +
  xlab("Quarters") +
  ylab("R-squared") +
  labs(title = "GDP R-squared") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(limits=c("H1","H2","H4", "H8"))

regression.fit
```



```{r regcoefficients, message = F, warnings = F, echo = F, fig.height=3, fig.width=6, fig.cap="Regressions' coefficients"}

regression.coefficients <- ggplot(results1, aes(x=row.names(results1), y=YIV_estimate))+
  geom_bar(stat="identity", fill="steelblue")+
  theme_bw()+
  xlab("Quarters") +
  ylab("Coefficients") +
  labs(title = "GDP coefficients") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(limits=c("H1","H2","H4","H8"))

regression.coefficients

```


\newpage

# Appendix C {#S:descriptive}


```{r, sum-stat,message = F, warnings = F,echo = F, fig.cap="Overview of main variables"}

summary_table %>%
  kbl(longtable=T, booktabs=T) %>%
  kable_styling() 

```



\newpage
# Appendix D {#S:appendixd}

Notes: The following regressions includes YIV, dummy and controls as independent variables. For the description of the variables in the output, please refer to Appendix \@ref(S:descriptive). The specification for the regression is the following:

\begin{equation}
\frac{1}{H} \sum_{j=1}^{j=H}log(1+GDP_{i,t+j})/H = \alpha_{H}+ \beta_{H} \sigma_{IV,t}^{INT} + Controls + Dummy +\varepsilon_{t+H}
\end{equation}




```{r OLS5, message = F, warnings = F,echo = F}
regr5 <- regrs(indep_vars=indep,interaction=F)
results5 <- regr_results(a=regr5) %>%
  round(2) %>%
  significance() %>%
    rename(" "=rowname)



results5  %>%
  kbl(booktabs = T,longtable=T, align="c", digits=2, caption="Regression with state-dependency") %>%
   kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
    column_spec(1:1, width="2in")%>%
       footnote(general = "*** - p<0.01, ** - p<0.05, * - p<0.1. Reported standard error is adjusted for heteroskedasticity")

#model5 <- lm(log_gdp ~ YIV + dum + YIV*dum + lag2 + DGS1 + TRM1012 + SRT03M + baa_aaa + VIX + housng + gz_spr + spy_logreturn, df)
#ols_vif_tol(model5)

# model6 <- lm(log_gdp ~  YIV + dum + YIV*dum + lag1 + lag2 + DGS1 + TRM1012 + SRT03M + baa_aaa + VIX + housng + gz_spr + spy_logreturn, df)
# ols_step_forward_p(model6)
# ols_step_best_subset(model6)
# ols_step_all_possible(model6)

```
\newpage

# Appendix E {#S:rmsfegraph}


```{r, rmsfeerrors, message = F, warnings = F,echo = F, fig.cap="Out-of-sample RMSFE for various estimations"}

df_results %>%
  kbl(longtable=T, booktabs=T) %>%
  kable_styling(full_width = TRUE) 

```

```{r, rmsfegraphs, message = F, warnings = F,echo = F, fig.cap="Out-of-sample RMSFE graphs"}
data <- melt(df_results)
data$rowid <- c("YIV", "YIV_Recessionary", "YIV_Expansionary" ,"Naive", "Naive_Recessionary", "Naive_Expansionary", "TRM", "CRS","Full model", "Full - reccessionary", "Full - expansionary")

ggplot(data, aes(variable, value, group=factor(rowid))) +
  geom_line(aes(color=factor(rowid))) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x="Time horizon", y="RMSFE value", color="Model") +
  facet_wrap( ~rowid)
#fig.cap"Out-of-sample RMSFE for various estimations

```
\newpage

# Appendix F {#S:predictedactuals}

The following figures display predicted vs actual values for 1) linear model, 2) random forest. For the estimations, the full model described has been used. Do we add the variables here?

```{r, pred-vs-actual-lm, message = F, warnings = F,echo = F, fig.cap="Predicted vs actual results (Linear model)"}


pred_vs_actual_graph(lm,"Linear model") 

```


```{r, pred-vs-actual-rf, message = F, warnings = F,echo = F, fig.cap="Predicted vs actual results (Random forest)"}


pred_vs_actual_graph(rf,"Random forest")


```

\newpage
# Appendix G {#S:rmsfelmsvsrf} 

The figure below displays RMSFEs for both linear model and Random Forest in 3 different panels: 1) with only expansionary observations, 2) with only recessionary observations as defined by NBER recessions and 3) the full-model.

```{r, RSMFE-lm-vs-rf, message = F, warnings = F,echo = F, fig.cap="RMSFE-s of linear model and random forest"}

ggplot(lm_rf_results, aes(variable, value, group=factor(Specification))) + geom_line(aes(color=factor(Specification))) +
  theme(legend.position="bottom") +
  labs(x="Time horizon", y="RMSFE", color="Model") + 
  facet_wrap(~period) +
  scale_color_manual(values=c("blue", "red")) +
  theme_bw()

```


\newpage


# Appendix H {#S:squarederrors} 
The figure below includes squarede erros for both models over all of the forecast horizons. Squared errors have been calculated as the squared difference of actual - predicted values.

```{r, squared-errors, message = F, warnings = F,echo = F, fig.cap="Squared errors"}
a <- c("OOS_error_lm","OOS_error_rf")


squared_error_plot(a)


```


\linespread{.75}\selectfont

\newpage

# Appendix I {#S:BSnote} 

**Formula for dependent variable as used in the paper where $GDP_{t+j}$ is the GDP year-on-year growth rate in quarter $t+j$.**
\begin{equation}
\frac{1}{h}\sum_{j=1}^{j=h} \ln (1 + GDP_{t+j})
\end{equation}

**For $h=1$**
\begin{align}
\ln (1 + GDP_{t+1}) & = \ln \left(1 + \frac{y_{t+1} - y_{t-3}}{y_{t-3}}\right) = \\
&= \ln \left(1 + \frac{y_{t+1}}{y_{t-3}-1} \right) = \ln \left(\frac{y_{t+1}}{y_{t-3}} \right) = \\
&= \ln y_{t+1} - \ln y_{t-3} = \\
&= \ln y_{t+1} - \ln y_{t} + \ln y_{t} - \ln y_{t-1} + \ln y_{t-1}  - \ln y_{t-2} + \ln y_{t-2} - \ln y_{t-3} = \\
&= (\ln y_{t+1} - \ln y_{t}) + (\ln y_{t} - \ln y_{t-1}) + (\ln y_{t-1}  - \ln y_{t-2}) + (\ln y_{t-2} - \ln y_{t-3}) = \\
&= \Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} + \Delta \ln y_{t-2}
\end{align}

**For $h=4$**
\begin{align}
&\frac{1}{4}( \ln (1 + GDP_{t+4}) + \ln (1 + GDP_{t+3}) +  \ln (1 + GDP_{t+2}) + \ln (1 + GDP_{t+1})) = \\
&= \frac{1}{4}(
\Delta \ln y_{t+4} + \Delta \ln y_{t+3} + \Delta \ln y_{t+2} + \Delta \ln y_{t+1} + \\ 
&+\Delta \ln y_{t+3} + \Delta \ln y_{t+2} + \Delta \ln y_{t+1} + \Delta \ln y_{t} +\\
&+\Delta \ln y_{t+2} + \Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} + \\
&+\Delta \ln y_{t+1} + \Delta \ln y_{t} + \Delta \ln y_{t-1} + \Delta \ln y_{t-2} + ) =\\
&= \frac{1}{4}( \Delta \ln y_{t+4} +2 \Delta \ln y_{t+3} + 3\Delta \ln y_{t+2} + 4\Delta \ln y_{t+1} + 3\Delta \ln y_{t} + 2\Delta \ln y_{t-1} + \Delta \ln y_{t-2}) 
\end{align}


**This formula is for average quarterly growth rate for $h=4$:**
\begin{align}
&\frac{1}{4}( \ln (1 + GDP_{t+4})) = \\
&= \frac{1}{4}(
\Delta \ln y_{t+4} + \Delta \ln y_{t+3} + \Delta \ln y_{t+2} + \Delta \ln y_{t+1})
\end{align}


**Formula for quarterly growth rate for $h=4$:**
\begin{align}
\Delta \ln y_{t+4} 
\end{align}

\newpage
\linespread{1}\selectfont

# Appendix J {#S:gdpversions}

Following figures describe the effect of averaging with the alternative variables of GDP discussed. As it can be seen, the variance reduces significantly between the two forecast period H1 and H8, which as well affects the RMSFEs calculated.


```{r, fig.height=4, fig.cap="Average quarterly growth rates of GDP h-quarters ahead"}
bsnote_graph(N,"GDP Growth (%)")
```


```{r, fig.height=4, fig.cap="Average quarterly year-on-year growth rates (as in the original paper"}
bsnote_graph(H,"GDP Growth (%)")
```

