---
title: "Results"
author: "Karel Räpp, Henry Enno Turu"
date: "29 11 2020"
output: 
  bookdown::pdf_document2:
    toc: no
csl: apa.csl
bibliography: library.bib
indent: yes
fontsize: 12pt
geometry: margin = 1in
link-citations: yes
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{float}
- \usepackage{amsmath}
- \DeclareMathOperator{\logit}{logit}
---

```{r resultimport, include=F, message = F, warnings = F,echo = F}
source("functions.R")
```


# Results

For preliminary analysis, we plot quarterly YIV with quarterly GDP growth rates to see whether visual patterns arise. As it can be seen in Figure \@ref(fig:YIV-gdp), YIV seems to have a negative correlation with GDP.  This relationship is especially profound during Global Financial Crisis (around 2008-2009) when YIV surges up while a considerable decline in GDP growth happens. This confirms our base for analysis as suggested by the literature review that indeed the treasury could have the predictive ability over GDP growth rate.

```{r, YIV-gdp, message=F, warnings=F, echo = F, fig.cap="GDP Growth(%) vs 5-year Treasury Implied Volatility"}
df %>%
  select(Date, GDP, YIV) %>%
  gather(key = "variable", value = "value", -Date) %>%
  ggplot(aes(x=Date, y=value)) +
    geom_line(aes(color = variable, linetype = variable)) +
   annotate("rect", xmin = as.Date("2001-04-01", "%Y-%m-%d"), xmax = as.Date("2001-10-01",  "%Y-%m-%d"), ymin = -Inf, ymax = Inf,alpha = 0.4, fill = "grey") +
    annotate("rect", xmin = as.Date("2008-01-01", "%Y-%m-%d"), xmax = as.Date("2009-04-01",  "%Y-%m-%d"), ymin = -Inf, ymax = Inf,alpha = 0.4, fill = "grey") +
    theme_bw() +
    scale_fill_manual('NBER recessions',
                      values = 'grey',  
                      guide = guide_legend(override.aes = list(alpha = 1))) +
    theme(legend.position = "bottom", legend.title = element_blank()) +
    labs(x="Date", y="Growth rate")
```

## In-sample regressions

We start our analysis by replicating the regressions in the paper by @Cremers2021, starting with regressing YIV to GDP growth throughout different rolling periods - i.e. from H=1 to H=8 quarterly GDP growth rolling averages (the regression formula and summary can be seen in Table \@ref(tab:OLS1)). For interpreting the regression results, the coefficient is multiplied by the standard deviation, and the result obtained is the impact on yearly GDP growth. Hence, as an example of H=1, the results implicate that one standard deviation increase in YIV results in a -1.03/4 * 1.31% = 0.34% decrease in GDP growth within the next quarter. For predicting 8 quarters ahead (2 years), one standard deviation increase in YIV results in a -0.6 * 2 * 1.31% = 1.57% decrease in GDP growth within the next 8 quarters. To illustrate the magnitude of this reduction, one should note that the average year-on-year growth rate in our sample is 2,5%.

Furthermore, it can be seen, YIV’s coefficients are significant throughout the prediction periods within 1% of confidence level. The model’s R-squared varies within the range of 36% for predicting 2 quarters ahead down to 20% for predicting 2 years ahead. Lastly, as an additional robustness check to ensure that YIV predicts GDP growth and not the other way around, we run the Granger causality test by which we indeed conclude that YIV granger-caused GDP growth.


\begingroup
\linespread{1.0}\selectfont



```{r OLS1, message = F, warnings = F,echo = F}
regr1 <- regrs(indep_vars=c("YIV"),interaction=F)
results1 <- regr_results(a=regr1) %>%
    round(2) %>%
    significance() %>%
    rename(" "=rowname)

results1 %>%
  kbl(booktabs = T, longtable=T, align="c", digits=2, caption="Regression output") %>%
  kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
     column_spec(1:1, width="2in")%>%
  footnote(general = "*** - p<0.01, ** - p<0.05, * - p<0.1. Reported standard error is adjusted for heteroskedasticity")

#grangertest(log_gdp ~ YIV, order=1, df)
```
\endgroup

Next, we add a dummy variable representing recessionary periods (according to the NBER classification), i.e. the dummy takes a value of 1 during recession and 0 during expansion. As it can be seen from the Table \@ref(tab:OLS2), the dummy’s coefficient is negative and significant at a 1% confidence level throughout all predicted time spans - nevertheless, the interaction term between YIV and dummy variable is insignificant throughout all forecast horizons. Hence, this means that the recessionary period only influences the intercept, not the slope of the variable. However, the inclusion of dummy decreased the significance of YIV while improving R-squared - 54% in predicting ahead GDP growth 4 quarters’ rolling averages when compared to 34% of respective YIV-only model. The latter indicates that there is a structural break in data during recessions and that using the full model to predict during recessionary periods could result in worse prediction accuracy.

\begingroup
\linespread{1.0}\selectfont



```{r OLS2, message = F, warnings = F,echo = F}
regr2 <- regrs(indep_vars=c("YIV", "dum"),interaction=T)
results2 <- regr_results(a=regr2) %>%
    round(2) %>%
    significance() %>%
    rename(" "=rowname)


results2  %>%
  kbl(booktabs = T,longtable=T, align="c", digits=2, caption="Regression with state-dependency") %>%
   kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
     column_spec(1:1, width="2in")%>%
       footnote(general = "*** - p<0.01, ** - p<0.05, * - p<0.1. Reported standard error is adjusted for heteroskedasticity")

```
\endgroup


Additionally, we constructed a regression with YIV and control variables as dependent variables - as it can be seen from the Appendix \@ref(S:appendixe) YIV is still highly significant throughout all of the forecasting horizons.
Finally, we combined the previous variables with all of the available control variables in @Cremers2021 into one regression equation (Appendix \@ref(S:appendixf). After including all the relevant control variables, the YIV remains significant at 5% in H4 and at 10% in H8. In this model, the regression results implicate that one standard deviation increase in YIV should result in a -0.35 * 1.31% = -0.46 % decrease in GDP growth within the next 4 quarters. Additionally, when predicting 8 quarters ahead, a one standard deviation increase in YIV results in a -0.34* 1.31% * 2 = 0.89% decrease in the next 8 quarters’ average annualized growth rate.


## Out of sample forecasting
### Full sample

We were not only interested in the in-sample performance of the variable. Hence, we constructed out-of-sample (OOS) regressions to compute RMSFE-s of full-sample and subsample models. It is important to note that from here on out, we use h-step forward-looking quarterly growth rates as a dependent variable (denoted as F1, F2, etc.) instead of the year-on-year averaged growth rates (denoted H1, H2, etc.). For a more detailed explanation on changing the dependent variable, please refer to the methodology section.
Thus, for the out-of-sample regressions, we use 5-year rolling windows to predict 1-8 quarters ahead. Looking at the full model’s predicted values and actual observations (see Appendix \@ref(S:predictedactuals)), it can be seen that the predicted values tend to differ more as the forecast horizon increases. While forecasting 1 period ahead, the predicted graph is fairly similar to the actual observations. For F4, two big forecast errors can be noticed.

This is consistent with the RMSFEs calculated (see Appendix \@ref(S:rmsfegraph)) - i.e RMSFE’s tend to increase with the forecast horizon, except for F2. In other words, the model's accuracy in predicting GDP growth got worse in predicting further time periods. Looking at performance of the full-model, it can be seen that it yields the highest forecast errors compared to individual panels. 

### Sub-sample OOS forecasting

Next, we wanted to compare the full-sample OOS RMSFE-s with the subsample OOS RMSFE-s. As it can be seen from the same Figure (\@ref(S:rmsfegraph)), during the recessionary period, the RMSFE is significantly higher when compared to the full-sample RMSFE - furthermore, this holds for all the different models.   

```{r subs, fig.height=3, fig.cap="Relative Recessionary & Expansionary RMSE"}
relative_rmsfe  <- relative_rmsfes

relative_rmsfe  %>%
  kbl(booktabs = T,longtable=T, align="c", digits=2, caption="Relative RMSFEs") %>%
   kable_styling(latex_options = c("striped"), full_width = TRUE) %>%
     column_spec(1:1, width="2in")

```

Table \@ref(tab:subs) describes subsample relative RMSFE within different forecasting periods. If the value is over 1, it indicates that the benchmark model (full sample model) has superior forecasting performance compared to the corresponding subsample model. 


## Out-of-sample forecasting with Random Forest


Lastly, we construct a RF model to see whether the forecasting accuracy can be improved. As it can be seen from Figure \@ref(fig:CSSFED-lm-rf) the overall performance of the RF model is better when compared to OLS across all of the prediction periods as indicated by the upward sloping graph (meaning that OLS's squared errors are larger than the respective squared errors of the RF model). Furthermore, the same conclusion is derived when looking at the Appendix \@ref(S:rmsfelmsvsrf) where it can be seen that the RF model significantly outperforms during the full sample, and also separately in both subset periods. Additionally, these results are consistent with Appendix \@ref(S:predictedactuals) and Appendix \@ref(S:squarederrors). The latter can be used to visually validate the difference between the accuracy of RF and linear model as during H4 and H8 forecasts as linear model's errors spike especially high after the 2008-2009 Financial crisis, which is not the case for the RF model. Also, this can be noted that on the CSSFED graph below since the bigger jumps tend to happen around recessionary periods.

```{r, CSSFED-lm-rf, message = F, warnings = F,echo = F, fig.height=4, fig.cap="Cumulative sum of squared forecast error differential (Linear model - Random Forest)"}
CSSFED_plot("lm_rf") 
```

In Figure \@ref(fig:var-imp), we have plotted the importance of different variables as extracted from the RF model. The figure shows on which variables the RF model relies the most to make predictions, i.e. which variables are the most important for the model's accuracy. As it can be seen, throughout different forecast horizons, the importance of the variables change - e.g. for H1 predictions, the most important variable is baa_aaa (yield spread between BAA and AAA yields) while for H8, the most important variable is TRM1006 (10 years and 6-month treasury yield spread). During H1 and H2, YIV is 2nd and 1st, respectively. However, during H4 and H8, the importance still exists but is among the lowest. Lastly, the dummy variable displays no importance for the RF model, except for 1 quarter ahead of predictions. 

```{r, var-imp, message= F, warnings = F,echo = F,  fig.cap="Variable importance"}
p1 <- plot(variable_importance(dep[1]), main="H1")
p2 <- plot(variable_importance(dep[2]), main="H2")
p3 <- plot(variable_importance(dep[3]), main="H4")
p4 <- plot(variable_importance(dep[4]), main="H8")
grid.arrange(p1, p2, p3, p4, nrow=2)

```
